A Critical Appraisal of the Zero-Multiple Method: Structural, Thermodynamic, Dielectric, and Dynamical Properties of a Water System

### 2014-12-05 writedown/zm/paper.water/main.tex
partially finish revising

%2multibyte Version: 5.50.0.2952 CodePage: 932
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
%\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
% \input{tcilatex}
% \input{tcilatex}

@@

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2952}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Thursday, November 13, 2014 17:19:51}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\exc}{\textrm{ex}}
\newcommand{\systemsa}{S_0}
\newcommand{\systemsb}{S_1}
\newcommand{\systemsbp}{S'_1}
\newcommand{\systemma}{M_0}
\newcommand{\systemmb}{M_1}
\newcommand{\systemmbp}{M'_1}
\newcommand{\systemla}{L_0}
\newcommand{\systemlbp}{L'_1}
\newcommand{\systemlb}{L_1}
% \input{tcilatex}
\begin{document}

\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
6, 100088 Beijing, China}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
Saitama 351-0198, Japan}
\author{Haruki Nakamura}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\date{\today}

@@

{\color{red} If we want to discuss the issue of cut-off method, a short
introduction of the group cut-off v.s.~the atom cut-off method. (will
discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
do you mean? {\color{red} I mean the explanation of group and atomistic
cut-off method. the traditional gromacs uses group cut-off as default. We
need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
matter for {traditional gromacs} will be discussed in Sec. IIIB, and the
relevant matter of ZM will be discussed around $\bigstar ${\ in Sec. IIIB.
If we feel the resulted descriptions are too detailed, they will go to SI.}] 
} [{\color{red} please see the red part in Sec. III B. The order of the
paragraphs are also rearranged.}][ {\color{blue} I added comments.}]

@@

[{%
\color{blue} COMMENT: I am confusing. Is "rcoulomb"="rlist" default in
gromacs? If so, "Gromacs by default uses the group cut-off scheme" is
correct. Or, here, you want to say the "neighbor list making" is done by
group cut-off? (I reread your "cutoff.pdf")} \recheck{
In the main text I only mention the ``group cut-off'' and ``atom cut-off'' and
put how to implement them in the Appendix.  So those who are not familiar with Gromacs would not be confused by the Gormacs terminology (e.g. rlist, rcoulomb, ...).
see the revise below:
}]

The neighbor lists were updated every 5 time-steps. The Gromacs
by default uses the group cut-off scheme, while the ZM method suggests an
atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between these
cut-off schemes is discussed in detail in e.g.~Ref.~\cite%
{hunenberger1998alternative,baumketner2009removing}. We adopted the atom
based cut-off scheme in the simulations using the SPME (short-range part)
and ZM electrostatic methods, \recheck{while group cut-off scheme for RF.
  We treated RF differently because the group cut-off scheme is the default scheme in Gromacs.}
\recheck{The implementation details of the atom cut-off scheme in Gromacs are proivded in Appendix.~\ref{app:cut-off}.}

% In order to mimic the atom cut-off scheme in
% the Gromacs group cut-off implementation, the radius for neighbor list
% updating was set ${0.3}$~nm larger than the cut-off radius (the maximum of
% Coulomb cut-off and the van der Waals cut-off).

% The \textquotedblleft 
% \texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used.[ {\color{blue} COMMENT:
% Yes,..., this is not easy to understand how we mimic AC. {\color{red} it
%   should be OK as it is now.}} {\color{blue} Please see COMMENT in SecII.}]

The short-range part of SPME method was cut-offed at $1.9$~nm, and was
smoothed in a shell of $0.05$~nm width by the Gromacs \textquotedblleft 
\texttt{pme-switch}\textquotedblright\ method. The reciprocal space grid
spacing was set to $0.06$~nm, with B-Spline interpolation order of $6$.
These parameters were chosen to be more accurate than the Gromacs default
choices (grid spacing $0.12$~nm and interpolation order $4$).
The conducting boundary condition was used with SPME.
The splitting parameter was optimized by the error estimate, which is
implemented in Gromacs by tool \textquotedblleft \texttt{g\_pme\_error}%
\textquotedblright ~\cite{wang2010optimizing}. The optimized real space and
reciprocal space force computing errors were equally distributed as $%
1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude of the forces are of
order $10^{2}$~kJ/(mol nm), this force computing precision almost reaches
the limit of the single-precision representation of the floating point
numbers. % [ {\color{blue} COMMENT: Did you use the
% conducting boundary conditions? (maybe it is default in gromacs.) Please
% state the thing.}]
\recheck{The ZM method was implemented in Gromacs with the tabulated electrostatic
interaction, and the interaction tables were generated by a home-made code.
The experimental dielectric consistency  $\varepsilon _{\text{rf}}=80$
was adopted for the RF method.}

% In the simulations using RF method, the electrostatic interactions were cut-off in the
% group manner (Gromacs default), so the radius for neighbor list updating is set identical to
% the cut-off radius. [{\color{blue} COMMENT: Is "rcoulomb"="rlist" default
%   for RF? If so, please describe it.} \recheck{Describing "rcoulomb"="rlist" by human languange} ]
% \recheck{We used $1.2$~nm for both of them}, and the experimental dielectric constant $%
% \varepsilon _{\text{rf}}=80$.

@@

It should be noticed that in the calculation of the chemical
potential, the energy correction plays an important role. In the case of $%
l=1 $, $\alpha =0.0\,\text{nm}^{-1}$, it contributes $-0.1$~kJ/mol to the
final result. By increasing $l$ or $\alpha $, this contribution becomes more
significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha =0.0\,\text{nm}%
^{-1}$, and $-1.0$~kJ/mol for $l=1$, $\alpha =2.0\,\text{nm}^{-1}$,
respectively. [{\color{blue}COMMENT: We will clarify what is the "energy
correction" after making SecII, and describe the relation to IPSp after
making Appendix B.}]

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level. 
{\color{red} This uncertainty is twice of the standard deviation of the
estimates (which are averages along MD trajectories) that is calculated by
the block average method~\protect\cite{janke2002statistical}.} [ {\ 
\color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
\color{blue} another COMMENT: In these figures, can we see the statistical
uncertainty of the pressure obtained by the SPME? Viz., I found no error
bars for SPME.} \recheck{NO SPME result is given in this figure, 1 Bar is the target pressure.}]}
\label{fig:pres-comp}
\end{figure}

@@

It should be noted that even with the system $L_{0}$ that contains 13824
water molecules, the fluctuation (measured by standard deviation) of the
pressure is roughly 100~Bar, which means that it is very difficult to
achieve very accurate estimate for this quantity.
\recheck{In practice a pressure
error of 20~Bar will only cause a
density deviation (calculated by the NPT simulations) of roughly 0.1\%.
Taking different orders ZM method at cut-off 1.2~nm for example,
the density deviations are 0.051\%, 0.061\%, 0.097\% and 0.146\% for $l=1,2,3$ and 4, respectively.
For $l\leq 3$ the pressure error is less than 20~Bar, while for $l=4$ the pressure error is less than 30~Bar (see Fig.~\ref{fig:pres-comp}).
}

[{\color{blue} COMMENT1: Can we have a
trajectory figure of the pressure? It will show that the fluctuation is
large and the 10 Bar error for ZM looks small. If there is a suitable one,
it may be good to put it in SI.} \recheck{Could you explain why? The SD should be enough for our purpose.}] [ {\color{blue} COMMENT2: Can we have some
data on the (mass) density? Some potential users of ZM\ may worry about the
deviation of the density from the reality due to the pressure error. I
remember that the density error for ZM was small. It is helpful to show that
the deviation of the density is sufficiently small. These two comments
indicates that one wants to feel how good or bad about the 10 Bar error.} \recheck{Done}]

@@

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$)
with $\alpha =0$\ and RF methods. It is observed from the figure that the
ZM RDFs are consist very well with the SPME RDF, except oscillations around
the cut-off radius. This oscillations are not so large, as the maximum
magnitude of the discrepancies from the SPME is about $1.9\%$
for $l=1$ and ${0.3\%}$ for $l=2$, % {[} {\color{blue}
% "$2\%"$ is just my guess. How about stating here the maximum error for
% individual $l$}]
but should be artificial. However, higher order
ZM method present lower amplitude oscillation, and when $l\geq 3$, the
improvement is dramatic and the oscillation is almost negligible.

{\color{red} Shall we comment here on the fact that group cut-off produces
smoother RDF? Add figures in Supplementary material {\color{blue} Do you
mean the reason of the goodness in RF?} {\color{red} Yes, shall we discuss
it? or it is too complicated and not very relevant to the current paper?}[} {%
\color{blue} It is preferable to write it if the reason of the goodness is
clear. Anyway, please describe.... This is the only matter ZM is inferior to
RF. So, it may be interesting if the reason is clear. } {\color{red} I
agree, if the reason is not clear for us, we should not touch this topic.}][ 
{\color{blue} COMMENT: Thank you very much for the O-O RDF. If you have time
to reconsider this issue, it may be useful to calculate the RDF with H-H
length (MD trajectory also remains). Deviations should be larger for H-H
than O-O, but this is my guess: (1) eventually COG-COG is near O-O, sorry I
did not notice.; (2) RDF deviations appear in 0.6 nm width around the cutoff
and the H-H length is just the twice of this 0.6 nm). Rather, the true
reason may be other, e.g., group cuotff MD scheme may intrinsically give the
accracy at least for RDF. }]

@@

At cut-off radius of 1.2~nm, the recommended choices of
parameters for TIP3P system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $%
l=2$ or $l=3$. Using these parameters, the ZM method achieves almost perfect
accuracy in computing the excess chemical potential, constant
volume/pressure heat capacity, isothermal compressibility, thermal expansion
coefficient, dielectric constant diffusion constant and viscosity. The order 
$l=2$ performs better in reproducing the pressure than $l=3$ (10
v.s.~17~Bar), but worse in calculating the RDF (0.2\% error v.s.~almost
negligible). Both of orders 2 and 3 are not sensitive to the splitting
parameter up to 1.0~$\text{nm}^{-1}$. Although further
increasing the splitting parameter will push the accuracy of RDF in case $%
l=2 $ to as high as $l=3$, the pressure accuracy decreases (anti-damping
effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is not recommended. It
should be noticed that the recommended parameters indicate $5$\% error
(largest) in calculating the Kirkwood-G factor for a larger system ($L_{1}$
containing 13,824 molecules).  If we seek more
accuracy for the G factor, we should use a larger cut-off radius at the
expense of the computational time. 
% Further increasing the splitting paraemter
% Optimal parameter value for the TIP3P system is thus $l=2,\alpha \leq 1$,
% where the error about $0.2\%$\  remains in the RDF. An
% alternative choice is $l=3,\alpha =0$, where the accuracy in the pressure is
% not the best but highly accurate RDF can be obtained.

@@

\section{Implementation of atom cut-off scheme in Gromacs}
\label{app:cut-off}

The Gromacs code 4.6 does not directly 
support the atomistic cut-off scheme for tabulated electrostatic interaction that is
needed for ZM method. The atom cut-off scheme can be implemented
by using the default ``\texttt{Group}'' neighbor searching method, while setting
the radius of neighbor list ``\texttt{rlist}'' 0.3~nm larger than the cut-off radius,
which is the maximum of the electrostatic cut-off ``\texttt{rcoulomb}'' and the van der Waals cut-off ``\texttt{rvdw}''.
Due to the buffering region that is of thickness 0.3~nm, the atom cut-off scheme in Gromacs is in general more expensive than the group cut-off scheme.

@@

In this section we provide the formula used for computing the benchmark
quantities. We assume that there are $N$ molecules in the water system. The
position and configuration of each molecule are fully described by $\{\vect r_{3i-2},\mathbf{\mathit{r}}_{3i-1},\mathbf{\mathit{r}}
_{3i}\},\,i\in 1,\cdots ,N$, and the corresponding velocities are denoted by 
$\{\mathbf{\mathit{v}}_{3i-2},\mathbf{\mathit{v}}_{3i-1},\mathbf{\mathit{v}}%
_{3i}\},\,i\in 1,\cdots ,N$. The mass of each atom is denoted by $m_{i}$.[ {%
\color{blue} minor: I like bold font a little bit for $\mathbf{\mathit{r}}${%
\ and }$\mathbf{\mathit{v}}${\ as in the first version, which is also seen
in }$\boldsymbol{\mu }_{i}${. (In particular, }$\mathbf{\mathit{r}}${\ seems
the distance, not vector. $\mathbf{\mathit{r}}$ appears below also. But if
you like this font, please use it also for $\boldsymbol{\mu }_{i}$)}} \recheck{I prefer the original one, I did not change it. I guess your program did it automatically. I suggest you compile this file with standard latex that dose not do any automatic change to the source file!. Now I change the one of them back, please see if it works on your machine}]

@@

The diffusion constant is calculated from the Einstein relation: 
\begin{align}
D = \lim_{t\rightarrow \infty}\frac {1}{6t} \langle \vert \mathbf{\mathit{r}}%
_i(t) - \mathbf{\mathit{r}}_i(0)\vert^2\rangle.
\end{align}
In practice, the mean-square-displacement $\langle\vert \mathbf{\mathit{r}}%
_i(t) - \mathbf{\mathit{r}}_i(0)\vert^2\rangle$ is calculated, then the
value is linearly fitted. It is calculated by NVT simulations of system $S_1$.

@@

>>>>

%2multibyte Version: 5.50.0.2952 CodePage: 932
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
%\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
% \input{tcilatex}
% \input{tcilatex}
% \input{tcilatex}

@@

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2952}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Monday, December 01, 2014 18:07:38}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\exc}{\textrm{ex}}
\newcommand{\systemsa}{S_0}
\newcommand{\systemsb}{S_1}
\newcommand{\systemsbp}{S'_1}
\newcommand{\systemma}{M_0}
\newcommand{\systemmb}{M_1}
\newcommand{\systemmbp}{M'_1}
\newcommand{\systemla}{L_0}
\newcommand{\systemlbp}{L'_1}
\newcommand{\systemlb}{L_1}

\begin{document}

\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{wang_han@iapcm.ac.cn}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
6, 100088 Beijing, China}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
Saitama 351-0198, Japan}
\author{Haruki Nakamura}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\date{\today}

@@

% {\color{red} If we want to discuss the issue of cut-off method, a short
% introduction of the group cut-off v.s.~the atom cut-off method. (will
% discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
% do you mean? {\color{red} I mean the explanation of group and atomistic
% cut-off method. the traditional gromacs uses group cut-off as default. We
% need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
% matter for {traditional gromacs} will be discussed in Sec. IIIB, and the
% relevant matter of ZM will be discussed around $\bigstar ${\ in Sec. IIIB.
% If we feel the resulted descriptions are too detailed, they will go to SI.}] 
% } [{\color{red} please see the red part in Sec. III B. The order of the
% paragraphs are also rearranged.}][ {\color{blue} I added comments.}]

@@

% [{\color{blue} COMMENT: I am confusing. Is "rcoulomb"="rlist" default in
% gromacs? If so, "Gromacs by default uses the group cut-off scheme" is
% correct. Or, here, you want to say the "neighbor list making" is done by
% group cut-off? (I reread your "cutoff.pdf")} {\color{red} In the main text I
% only mention the \textquotedblleft group cut-off\textquotedblright\ and
% \textquotedblleft atom cut-off\textquotedblright\ and put how to implement
% them in the Appendix. So those who are not familiar with Gromacs would not
% be confused by the Gormacs terminology (e.g. rlist, rcoulomb, ...). see the
% revise below: }][ {\color{blue} I see and also modified. check it.]}

The neighbor lists were updated every 5 time-steps. The Gromacs by default
uses the group cut-off scheme, while the ZM method recommends
an atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between these cut-off
schemes is discussed in detail in e.g.~Ref.~\cite%
{hunenberger1998alternative,baumketner2009removing}. We adopted the atom
based cut-off scheme in the simulations using the SPME (short-range part)
and ZM electrostatic methods. The implementation details of the
atom cut-off scheme in Gromacs are provided in Appendix.~\ref{app:cut-off}.
The ZM method was implemented in Gromacs with the tabulated electrostatic
interaction, and the interaction tables were generated by a home-made code.

We treated the RF with the group cut-off scheme because the
group cut-off scheme is the default scheme in Gromacs. The experimental
dielectric consistency $\varepsilon _{\text{rf}}=80$ was adopted for the RF
method.
% In order to mimic the atom cut-off scheme in
% the Gromacs group cut-off implementation, the radius for neighbor list
% updating was set ${0.3}$~nm larger than the cut-off radius (the maximum of
% Coulomb cut-off and the van der Waals cut-off). 
% The \textquotedblleft 
% \texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used.[ {\color{blue} COMMENT:
% Yes,..., this is not easy to understand how we mimic AC. {\color{red} it
%   should be OK as it is now.}} {\color{blue} Please see COMMENT in SecII.}]

The short-range part of SPME method was cut-offed at $1.9$~nm, and was
smoothed in a shell of $0.05$~nm width by the Gromacs \textquotedblleft 
\texttt{pme-switch}\textquotedblright\ method. The reciprocal space grid
spacing was set to $0.06$~nm, with B-Spline interpolation order of $6$.
These parameters were chosen to be more accurate than the Gromacs default
choices (grid spacing $0.12$~nm and interpolation order $4$). The conducting
boundary condition was used with SPME. The splitting parameter was optimized
by the error estimate, which is implemented in Gromacs by tool
\textquotedblleft \texttt{g\_pme\_error}\textquotedblright ~\cite%
{wang2010optimizing}. The optimized real space and reciprocal space force
computing errors were equally distributed as $1.4\times 10^{-4}$~kJ/(mol
nm). Since the magnitude of the forces are of order $10^{2}$~kJ/(mol nm),
this force computing precision almost reaches the limit of the
single-precision representation of the floating point numbers. 
% [ {\color{blue} COMMENT: Did you use the
% conducting boundary conditions? (maybe it is default in gromacs.) Please
% state the thing.}]
% In the simulations using RF method, the electrostatic interactions were cut-off in the
% group manner (Gromacs default), so the radius for neighbor list updating is set identical to
% the cut-off radius. [{\color{blue} COMMENT: Is "rcoulomb"="rlist" default
%   for RF? If so, please describe it.} \recheck{Describing "rcoulomb"="rlist" by human languange} ]
% \recheck{We used $1.2$~nm for both of them}, and the experimental dielectric constant $%
% \varepsilon _{\text{rf}}=80$.

@@

It should be noticed that in the calculation of the chemical potential, the
energy correction plays an important role. In the case of $l=1$, $\alpha
=0.0\,\text{nm}^{-1}$, it contributes $-0.1$~kJ/mol to the final result. By
increasing $l$ or $\alpha $, this contribution becomes more significant, and
reaches $-0.6$~kJ/mol for $l=4$, $\alpha =0.0\,\text{nm}^{-1}$, and $-1.0$%
~kJ/mol for $l=1$, $\alpha =2.0\,\text{nm}^{-1}$, respectively. [{%
\color{blue}COMMENT: We will clarify what is the "energy correction" after
making SecII, and describe the relation to IPSp after making Appendix B.}]

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level. 
{\color{red} This uncertainty is twice of the standard deviation of the
estimates (which are averages along MD trajectories) that is calculated by
the block average method~\protect\cite{janke2002statistical}.}
% [ {\ 
% \color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
% \color{blue} another COMMENT: In these figures, can we see the statistical
% uncertainty of the pressure obtained by the SPME? Viz., I found no error
% bars for SPME.} {\color{red} NO SPME result is given in this figure, 1 Bar
% is the target pressure.}][{\color{blue} Can I konw the the statistical
% uncertainty of the pressure obtained by the SPME?}]
}
\label{fig:pres-comp}
\end{figure}

@@

It should be noted that even with the system $L_{0}$ that contains 13824
water molecules, the fluctuation (measured by standard deviation) of the
pressure is roughly 100~Bar, which means that it is very difficult to
achieve very accurate estimate for this quantity.  In practice a
pressure error of 20~Bar will only cause a density deviation (calculated by
the NPT simulations) of roughly 0.1\%. Taking different orders ZM method at
cut-off 1.2~nm for example, the density deviations are 0.051\%, 0.061\%,
0.097\% and 0.146\% for $l=1,2,3$ and 4, respectively. For $l\leq 3$ the
pressure error is less than 20~Bar, while for $l=4$ the pressure error is
less than 30~Bar (see Fig.~\ref{fig:pres-comp}).

% [{\color{blue} {COMMENT1:} Can we have a trajectory figure of the pressure?
% It will show that the fluctuation is large and the 10 Bar error for ZM looks
% small. If there is a suitable one, it may be good to put it in SI.} {%
% \color{red} Could you explain why? The SD should be enough for our purpose.}%
% ] [ {\color{blue} COMMENT2: Can we have some data on the (mass) density?
% Some potential users of ZM\ may worry about the deviation of the density
% from the reality due to the pressure error. I remember that the density
% error for ZM was small. It is helpful to show that the deviation of the
% density is sufficiently small. These two comments indicates that one wants
% to feel how good or bad about the 10 Bar error.} {\color{red} Done}][ {%
% \color{blue} Thank you very much for your consideration of the density. {%
% COMMENT1: please see my question in the last page. COMMENT2: The deviation
% of the pressure between the ZM and PME should be due to this density
% deviation between the ZM and PME (0.1\%). Namely {0.1\% density deviation
% should cause 10 atm deviation.}\ How about this confirmation? ---The
% pressure by ZM\ in figs1\&2 was calculated with the NTV MD where the cell
% size was determined by the \textit{PME} NTP. So, if we will do NTV MD with
% the cell size determined by the \textit{ZM} NTP (which was used to calculate
% the current density), and if we calculate the pressure by ZM with this new
% NTV, then we should have 1 atm pressure for may cutoff lengths. If this is
% true, then we can show that the 10 atm deviation from the PME is not the
% serious problem but a tiny density deviation issue.--- How about this idea? }%
% }]

@@

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
) with $\alpha =0$\ and RF methods. It is observed from the figure that the
ZM RDFs are consist very well with the SPME RDF, except oscillations around
the cut-off radius. This oscillations are not so large, as the maximum
magnitude of the discrepancies from the SPME is about $1.9\%$ for $l=1$ and $%
{0.3\%}$ for $l=2$, % {[} {\color{blue}
% "$2\%"$ is just my guess. How about stating here the maximum error for
% individual $l$}]
but should be artificial. However, higher order ZM method present lower
amplitude oscillation, and when $l\geq 3$, the improvement is dramatic and
the oscillation is almost negligible. \recheck{The RF RDF is more accurate than the ZM ones,
this is mainly because of the group cut-off used in simulating with RF. When changing
the cut-off scheme to atom scheme, the accuracy is RF is roughly same as ZM $l=1$ (see SI).
We could not explain the reason, but the numerical evidence suggests if only the RDF is
of interest, a group cut-off scheme or higher order of ZM is preferable.
}

% {\color{red} Shall we comment here on the fact that group cut-off produces
% smoother RDF? Add figures in Supplementary material {\color{blue} Do you
% mean the reason of the goodness in RF?} {\color{red} Yes, shall we discuss
% it? or it is too complicated and not very relevant to the current paper?}[} {%
% \color{blue} It is preferable to write it if the reason of the goodness is
% clear. Anyway, please describe.... This is the only matter ZM is inferior to
% RF. So, it may be interesting if the reason is clear. } {\color{red} I
% agree, if the reason is not clear for us, we should not touch this topic.}][ 
% {\color{blue} COMMENT: Thank you very much for the O-O RDF. If you have time
% to reconsider this issue, it may be useful to calculate the RDF with H-H
% length (MD trajectory also remains). Deviations should be larger for H-H
% than O-O, but this is my guess: (1) eventually COG-COG is near O-O, sorry I
% did not notice.; (2) RDF deviations appear in 0.6 nm width around the cutoff
% and the H-H length is just the twice of this 0.6 nm). Rather, the true
% reason may be other, e.g., group cuotff MD scheme may intrinsically give the
% accracy at least for RDF. }][{\color{blue} COMMENT: Thank you very much for
% the HH trial. The reason may be other. Since we do not have the reason why
% RF was so good, one choice is the deletion of the RF data in the RDF. How do
% you think about it?}]

@@

At cut-off radius of 1.2~nm, the recommended choices of parameters for TIP3P
system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $l=2$ or $l=3$. Using
these parameters, the ZM method achieves almost perfect accuracy in
computing the excess chemical potential, constant volume/pressure heat
capacity, isothermal compressibility, thermal expansion coefficient,
dielectric constant diffusion constant and viscosity. The order $l=2$
performs better in reproducing the pressure than $l=3$ (10 v.s.~17~Bar), but
worse in calculating the RDF (0.2\% error v.s.~almost negligible). Both of
orders 2 and 3 are not sensitive to the splitting parameter up to 1.0~$\text{%
nm}^{-1}$. Although further increasing the splitting parameter will push the
accuracy of RDF in case $l=2 $ to as high as $l=3$, the pressure accuracy
decreases (anti-damping effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is
not recommended. It should be noticed that the recommended parameters
indicate $5$\% error (largest) in calculating the Kirkwood-G factor for a
larger system ($L_{1}$ containing 13,824 molecules). If we seek more
accuracy for the G factor, we should use a larger cut-off radius at the
expense of the computational time. 
% Further increasing the splitting paraemter
% Optimal parameter value for the TIP3P system is thus $l=2,\alpha \leq 1$,
% where the error about $0.2\%$\  remains in the RDF. An
% alternative choice is $l=3,\alpha =0$, where the accuracy in the pressure is
% not the best but highly accurate RDF can be obtained.

@@

\section{Implementation of atom cut-off scheme in Gromacs}

\label{app:cut-off}

The Gromacs code 4.6 does not directly support the atomistic cut-off scheme, 
{\color{blue}which is recommended in the ZM method, in }using tabulated
electrostatic interaction. The atom cut-off scheme can be implemented by
using the default \textquotedblleft \texttt{Group}\textquotedblright\
neighbor searching method, while setting the radius of neighbor list
\textquotedblleft \texttt{rlist}\textquotedblright\ 0.3~nm larger than the
cut-off radius, which is the maximum of the electrostatic cut-off
\textquotedblleft \texttt{rcoulomb}\textquotedblright\ and the van der Waals
cut-off \textquotedblleft \texttt{rvdw}\textquotedblright . Due to the
buffering region that is of thickness 0.3~nm, the atom cut-off scheme in
Gromacs is in general \recheck{twice} expensive \recheck{in computing the electrostatic interaction} as the group cut-off scheme.
\recheck{It should be pointed out that this implementation is not optimal,
  when the gromacs build-in atom cut-off scheme supports the tablulated potential, we expect better performance of ZM method.}
% {%
% \color{blue}How much? (just my interest)}

@@

In this section we provide the formula used for computing the benchmark
quantities. We assume that there are $N$ molecules in the water system. The
position and configuration of each molecule are fully described by $\{%
\mathbf{\mathit{r}}_{3i-2},\mathbf{\mathit{r}}_{3i-1},\mathbf{\mathit{r}}%
_{3i}\},\,i\in 1,\cdots ,N$, and the corresponding velocities are denoted by 
$\{\mathbf{\mathit{v}}_{3i-2},\mathbf{\mathit{v}}_{3i-1},\mathbf{\mathit{v}}%
_{3i}\},\,i\in 1,\cdots ,N$. The mass of each atom is denoted by $m_{i}$.
% [ {%
% \color{blue} minor: I like bold font a little bit for $\mathbf{\mathit{r}}${%
% \ and }$\mathbf{\mathit{v}}${\ as in the first version, which is also seen
% in }$\boldsymbol{\mu }_{i}${. (In particular, }$\mathbf{\mathit{r}}${\ seems
% the distance, not vector. $\mathbf{\mathit{r}}$ appears below also. But if
% you like this font, please use it also for $\boldsymbol{\mu }_{i}$)}} {%
% \color{red} I prefer the original one, I did not change it. I guess your
% program did it automatically. I suggest you compile this file with standard
% latex that dose not do any automatic change to the source file!. Now I
% change the one of them back, please see if it works on your machine}][ {%
% \color{blue} Sorry, maybe this is just the problem of my program, now I can
% see }$\mathbf{\mathit{r}}_{3i-2}${\ to be bold in your original pdf.}]

@@

The diffusion constant is calculated from the Einstein relation: 
\begin{align}
D = \lim_{t\rightarrow \infty}\frac {1}{6t} \langle \vert \mathbf{\mathit{r}}%
_i(t) - \mathbf{\mathit{r}}_i(0)\vert^2\rangle.
\end{align}
In practice, the mean-square-displacement $\langle\vert \mathbf{\mathit{r}}%
_i(t) - \mathbf{\mathit{r}}_i(0)\vert^2\rangle$ is calculated, then the
value is linearly fitted. It is calculated by NVT simulations of system $S_1$%
.

@@

{\color{blue} Question1: I see that the statistical uncertainty is twice of
the standard deviation of time series.\ Let $\{A(x(t),p(t))\}_{t\in \Lambda }
${\ be time series of physical quantity }$A(x,p)${. Then I want to confirm
how you defined the average and the standard deviation. (i) Are they for }$%
\{A(x(t),p(t))\}_{t\in \Lambda }${\ itself? (ii) }Or are they {for }$\left\{ 
\frac{1}{t}\int_{0}^{t}A(x(s),p(s))ds\right\} _{t\in \Lambda }${? }}

{\color{blue}Maybe (ii) is correct. But "100~Bar" in the description "the
fluctuation (measured by standard deviation) of the pressure is roughly
100~Bar" should come from (i). If so, I proposed the presentation of the
trajectory of pressures $\{P(x(t),p(t))\}_{t\in \Lambda }$ in SI.}

{\color{blue}Question2 (this is just from my interest): When you did the ZM
NTP with P-R method, how was the cell shape? You obtained the good density,
but how about the cell deformation? Was it keep almost the cubic structure?}
